\documentclass[a4paper, 11pt]{article}
\usepackage[a4paper, left=20mm, right=10mm, top=20mm, bottom=20mm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}

\definecolor{linkcolor}{HTML}{799B03} % цвет ссылок
\definecolor{urlcolor}{HTML}{799B03} % цвет гиперссылок
 
\hypersetup{pdfstartview=FitH,  linkcolor=linkcolor,urlcolor=urlcolor, colorlinks=true}
\hyphenpenalty=10000
\hbadness=10000
\pagestyle{empty}

\begin{document}
\begin{center}
    \huge\textbf{Tyulbashev Vladislav Sergeevich}\\
\end{center}
\null\hfill GitHub: \textbf{vtyulb} \\
\null\hfill Habr: \textbf{vtyulb} \\
\null\hfill Telegram: \textbf{vtyulb} \\
\null\hfill Mail: \textbf{vtyulb@vtyulb.ru} \\

\section*{} {
    \subsection*{Yandex 2018 -- 2022} {
        HighLoad, DevOps, C++. Senior Software Developer (G17). \\
        \\
        From autumn 2021: search department, realtime data delivery team. \\
        Yt database and yandex s3--compatible storage. Kubernetes \& docker alternatives. \\
        Our product is a specific database for Yandex Search and Yandex Direct. \\
        It serves 10 mil+ rps and has the ability to rollback for up to 3 hours almost instantly. \\
        \\
        Till autumn 2021: news department, infrastructure group, runtime team. \\
        Proprietary stack, yandex internal technologies -- L3, L7, AppHost. \\
        Databases ydb, yt, redis, zookeeper. Kubernetes \& docker alternatives. \\
        \\
        In both teams I have been developing backend business logic and was responsible for duty shifts. \\
        There was also a lot of production configuration and highload services debugging.
    }
        
    \subsection*{Diaprom 2017 -- 2018} {
        Analytical software for nuclear power plants. Qt/C++, QML, microservices \\
        \href{http://www.diaprom.com/}{http://www.diaprom.com}
    }
    
    \subsection*{GitHub} {    
        BSA-Analytics, 2014 -- 2017 \\
        BSA telescope data processing. Qt/C++ \\
        \href{https://bsa-analytics.prao.ru/project/bsa-analytics}{https://bsa-analytics.prao.ru/project/bsa-analytics} \\ \\
        QLiveBittorrent, 2013 \\
        Torrent client with realtime opening feature. Qt/C++, FUSE, libtorrent \\
        \href{https://habr.ru/post/185770}{https://habr.ru/post/185770}\\ \\
        Labyrus, 2012 -- 2013 \\
        Network game based on it's own engine. Qt/C++, OpenGL \\
        \href{https://habr.ru/post/177807}{https://habr.ru/post/177807}\\ \\
    }
    
    \subsection*{About me} {
        Prizewinner of All-Russian programming Olympiad for schoolchildren 2012, 2013. \\
        I'm searching for difficult C++ projects on a modern technology stack. Relocation preferred. \\
        \href{https://vtyulb.ru}{https://vtyulb.ru}
    }
}

\end{document}
